Placing the spotted T Tauri star LkCa 4 on an HR diagram

### 2016-08-15 document/ms.tex
Get rid of all V est for simplicity

Some care should be taken when directly comparing results between the ESPaDOnS and IGRINS spectra since they were not taken at the same time.  These spectra have comparable albeit different $V_{\rm est}$ of 12.90 and 12.83 for the ESPaDOnS and IGRINS spectra respectively.  Assuming the areal coverage fraction of spots was the same or greater during the ESPaDOnS spectrum acquisition, the optical bands and short-wavelength end of $H$-band are relatively insensitive to the spectral signatures of starspots in this system.  The long wavelength portion of $H-$band and all of $K-$band are more sensitive to starspot spectral signatures than the shorter wavelength portions.

@@

Best fit values for the stellar parameters summarized are listed in Table \ref{tbl_adopted_props}.  Remarkably, the filling factor of starspots exceeds 50\% with a best fit value of $f_{\Omega}=75\pm 10 \% $.

@@

In the previous section, we established that the high resolution optical and near-IR spectra of LkCa 4 may be explained by a two-temperature photosphere.  In this section, we use testable predictions from this fit to demonstrate that the fit reasonably matches spectral features and their rotational modulation.  We adopt the best-fit two temperature model to the IGRINS spectrum, with components of 2750 K covering 80\% of the visible stellar surface and 4100 K covering 20\% of the stellar surface.  The IGRINS spectrum occurred when LkCa 4 had an estimated brightness of $V_{\rm est}=12.84$ mag.  These parameters are selected without any adjustments to attempt to improve fits to the SED or broadband spectra.

>>>>

Some care should be taken when directly comparing results between the ESPaDOnS and IGRINS spectra since they were not taken at the same time.  These spectra have comparable albeit different estimated $V-$band magnitudes of 12.90 and 12.83 for the ESPaDOnS and IGRINS spectra respectively.  Assuming the areal coverage fraction of spots was the same or greater during the ESPaDOnS spectrum acquisition, the optical bands and short-wavelength end of $H$-band are relatively insensitive to the spectral signatures of starspots in this system.  The long wavelength portion of $H-$band and all of $K-$band are more sensitive to starspot spectral signatures than the shorter wavelength portions.

@@

Best fit values for the stellar parameters summarized are listed in Table \ref{tbl_adopted_props}.  Remarkably, the filling factor of starspots exceeds 50\% with a best fit value of $f_{\Omega}=80\pm 5 \% $.

@@

In the previous section, we established that the high resolution optical and near-IR spectra of LkCa 4 may be explained by a two-temperature photosphere.  In this section, we use testable predictions from this fit to demonstrate that the fit reasonably matches spectral features and their rotational modulation.  We adopt the best-fit two temperature model to the IGRINS spectrum, with components of 2750 K covering 80\% of the visible stellar surface and 4100 K covering 20\% of the stellar surface.  The IGRINS spectrum occurred when LkCa 4 had an estimated brightness of $V=12.84$ mag.  These parameters are selected without any adjustments to attempt to improve fits to the SED or broadband spectra.
